The Effectiveness of Strategies to Contain SARS-CoV-2: Testing, Vaccinations, and NPIs

### 2022-03-08 src/paper/model/testing.tex
Refer to sensitivity robustness check when citing Smith2021.

In contrast to PCR tests, rapid tests are not perfect and can be falsely positive or
falsely negative. While the specificity of rapid tests is calibrated at 99.4\%
\citep{Bruemmer2021}, their sensitivity strongly depends on the timing of the rapid test
relative to the start of infectiousness \citep{Smith2021}. Before the onset of
infectiousness the sensitivity is very low (35\%). On the first day of infectiousness it
is much higher (88\%) but still lower than during the remaining infectious period (92\%).
After infectiousness stops, the sensitivity drops to 50 \%.

>>>>

In contrast to PCR tests, rapid tests are not perfect and can be falsely
positive or falsely negative. While the specificity of rapid tests is calibrated
at 99.4\% \citep{Bruemmer2021}, their sensitivity strongly depends on the timing
of the rapid test relative to the start of infectiousness. We follow
\cite{Smith2021} for our main results: Before the onset of infectiousness the
sensitivity is very low (35\%). On the first day of infectiousness it is much
higher (88\%) but still lower than during the remaining infectious period
(92\%). After infectiousness stops, the sensitivity drops to 50\%. We show that
our results are robust to more conservative assumptions in
Section~\ref{subsec:robustness_rapid_test_sensitivity}.

### 2022-03-08 src/paper/report.tex
Refer to sensitivity robustness check when citing Smith2021.

We include two types of tests. Polymerase chain reaction (PCR) tests reveal with
certainty whether an individual is infected or not; they are scarce and require at least
one day to be processed. In contrast, rapid antigen tests yield immediate results.
Specificity and sensitivity of these tests is set according to data analyzed in
\cite{Bruemmer2021, Smith2021}; sensitivity depends on the timing of the test relative
to the onset of infectiousness. Figure~\ref{fig:model_rapid_tests} shows our model for
rapid test demand. Schools may require staff and students to be tested regularly. Rapid
tests may be offered by employers to on-site workers. Individuals may demand tests for
private reasons, which include having plans to meet other people, showing symptoms of
CoViD-19, and a household member having tested positively for the virus. We endow each
agent with an individual compliance parameter. This parameter determines whether she
takes up rapid tests. Positive tests and symptoms lead most individuals to reduce their
contacts.

>>>>

We include two types of tests. Polymerase chain reaction (PCR) tests reveal with
certainty whether an individual is infected or not; they are scarce and require
at least one day to be processed. In contrast, rapid antigen tests yield
immediate results. Specificity and sensitivity of these tests is set according
to data analyzed in \cite{Bruemmer2021, Smith2021}; sensitivity depends on the
timing of the test relative to the onset of infectiousness (we show our results
are robust to more conservative assumptions in
Section~\ref{subsec:robustness_rapid_test_sensitivity}).
Figure~\ref{fig:model_rapid_tests} shows our model for rapid test demand.
Schools may require staff and students to be tested regularly. Rapid tests may
be offered by employers to on-site workers. Individuals may demand tests for
private reasons, which include having plans to meet other people, showing
symptoms of CoViD-19, and a household member having tested positively for the
virus. We endow each agent with an individual compliance parameter. This
parameter determines whether she takes up rapid tests. Positive tests and
symptoms lead most individuals to reduce their contacts.
